Thesis Title

### 2022-06-05 chapters/discussion.tex
Updates from Overleaf

Crowdsourcing for better standards represents a viable way to adopt better practices for the use of metagenomics in clinical microbiology. In Chapter \ref{ch:paper7}

>>>>

The term ‘crowdsourcing’ is used to describe systems for accomplishing directed work that requires human intelligence. These human-powered systems are built to solve discrete tasks with clear end points \citep{good_crowdsourcing_2013}. Crowdsourcing for better standards represents a viable way to adopt better practices for the use of metagenomics in clinical microbiology.

Different forms of crowdsourcing were successfully applied to address key problems in bioinformatics \citep{good_crowdsourcing_2013, connor_ncbis_2019, powell_organizing_2021}. Chapter \ref{ch:paper7} represents a proof of concept based on our experiences with developing software tests during a hackathon organised prior to the ASM Conference on Rapid Applied Microbial Next-Generation Sequencing and Bioinformatic Pipelines (ASM NGS) in 2020. In the end, we defined a set of
seven recommendations for researchers in microbial bioinformatics looking to develop software tests. Although limited to software testing, it represents a viable form of engaging the community in order to uphold new standards.

In the application of metagenomics to clinical diagnostics, we have discussed major pitfalls that require not only expert human input, but also a wide adoption by the community. Crowdsourcing generally begins where automation fails, and this is where initiatives such as hackathons represents a fundamental change in the way that scientific work is performed and distributed within the community. Recalling the original definition, crowdsourcing is a shift from work done in-house to work done in the open by anyone that is able. This means not only that we can often solve more problems more efficiently, but also that different people are solving them. Ultimately, is through crowdsourcing that the fastest and most efficient way can be applied to change golden standards, adopt new paradigms and ensure that the necessary conditions are widely spread.
